Data Preparation

### 2019-01-10 Data Preparation.Rmd
text AoD

# Variable Engineering
##Course Data
### AoD
In this analysis, we conside that a course can cover an AoD in two ways: a course covers an AoD if one of its ILOs covers it or if one of its assessments cover it. For instance, if one of the ILO of a course states that the students will learn to analyze empirical data in the context of academic research, then the course in question covers the AoD `Research Skills`; and if one of the assessment is a group presentation, then the course also covers the AoD `Collaborative Skills` and `Communication Skills`.

>>>>

# Variable Engineering
##Course Data
### AoD
In this analysis, we conside that a course can cover an AoD in two ways: a course covers an AoD if one of its ILOs covers it, or if one of its assessments cover it. For instance, if one of ILO of a course states that the students will learn to analyze empirical data in the context of academic research, then the course in question covers the AoD `Research Skills`; and if one of the assessment is a group presentation, then the course also covers the AoD `Collaborative Skills` and `Communication Skills`.
